Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-09-14 ms.tex
Finished edits up to Monte Carlo section - rewriting x_peak, doppler core boundary section

\subsection{Scaling with Line Center Optical Depth}
To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the $\tau_0$ is large and thus $J_{\rm bc}$ will be considerably larger than $H_{\rm bc}$. We obtain the proportionality
\be \label{eq:hbc_scaling}
\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
\ee
Thus, the fractional importance of the corrective frequency-dependent boundary condition term scales as the inverse cube root of the damping parameter $a$ times the line-center optical depth $\tau_0$. At very large optical depths, it is expected that the corrective term will be small, but will become increasingly important in less optically thick media.

The location of the spectral peak of the distribution is
\be \label{eq:tau_peak_scaling}
x_0 &\propto& \left(a\tau_0\right)^{1/3}.
\ee
This predicts that the characteristic photon frequency in Doppler widths should scale as the cube root of the parameter $a$ multiplied by the line center optical depth $\tau_0$, indicating the location of the spectral peaks on either side of line center --- the locations where the photons most readily escape. Since our derivations were performed assuming a Lorentzian line profile (see Appendix \ref{app:rteqn_derivation}), our solutions are technically only valid in the line wing, where the Doppler component of the line profile is small. Since our choice of the damping parameter $a$ is constant, the solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large optical depths. For \lya and a hydrogen gas of temperature $T=10^4$ K, the damping parameter $a = \Gamma / (4\pi\Delta)$ is equal to $4.72\times 10^{-4}$ in CGS units. Thus, the value of $\tau$ at which the Doppler and Lorentzian components of the line wing are equal is $\tau_{\rm cw}=7.3\times10^4$. Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.

>>>>

\subsection{Scaling with Line Center Optical Depth}
To examine the relative size of the correction term $H_{\rm bc}$ as compared to $H_0$, we consider the case where the $\tau_0$ is large and thus $J_{\rm bc} \gg H_{\rm bc}$. We obtain the proportionality
\be \label{eq:hbc_scaling}
\frac{H_{\rm bc}(R, \sigma)}{H_0(R, \sigma)} \propto \frac{1}{(a\tau_0)^{1/3}}.
\ee
Thus, the fractional importance of the correct frequency-dependent boundary condition term $H_{\rm bc}$ scales as $(a\tau_0)^{-1/3}$. At very large $\tau_0$, it is expected that the correction term will be small, but will become increasingly important as $\tau_0$ decreases.

The location of the spectral peak of the distribution is
\be \label{eq:tau_peak_scaling}
x_{\rm peak} {\sim} \left(a\tau_0\right)^{1/3}.
\ee
The solutions of the transfer equation will perform best when the peaks of the spectral energy distribution lie well outside of the Doppler core, e.g., for large $\tau_0$. For \lya and H atoms with $T=10^4$ K, the damping parameter is $a = \Gamma / (4\pi\Delta) = 4.72\times 10^{-4}$. Thus, the value of $x$ at which the Doppler and Lorentzian components of the line wing are equal is $x_{\rm cw}=3.3$. Setting $x_{\rm cw} = x_{\rm peak}$ and solving for $\tau_0$ gives the value of the line-center optical depth at which the core of the line moves into the peak of the spectrum, which is $\tau_{\rm cp}=7.3\times10^4$. Solutions derived assuming a Lorentzian line profile $\phi(x) \approx a/(\pi x^2)$ are expected to fail for lower line center optical depths where the peak of the spectrum lies near the core and improve for larger optical depths where the spectral peak is well outside of the line core.
